Fair Queuing Aware Congestion Control

### 2022-06-11 sample/tex/paper.tex
Paper fix

\begin{table}
\begin{minipage}{\columnwidth}
\centering
\begin{tabular}{| r | r | r |}
\hline
& Link utilization & Queuing delay \\ \hline
Newreno & 95.6\% & 10.5 ms \\ \hline
Tonopah & 94.3\% & 33.6 ms \\ \hline
% p-value\protect\footnote{Using Welch's t-test} & 0.86 & $1.9 \times 10^{-6}$ \\ \hline
% $\frac{\text{Newreno}}{\text{Tonopah}}$ & 103\% & 321\% \\ \hline
\end{tabular}
\caption{Newreno's link utilization is 103\% Tonopah's. But the \textbf{queuing delay} of Newreno is \textbf{321\%} Tonopah's. This means that Tonopah can deliver the same throughput while cause a lot less queuing delay. The differences in the throughput of Newreno and Tonopah are not significant (p-value\protect\footnote{Using Welch's t-test} $> 0.05$) while the differences in \textbf{queuing delay} are \textbf{highly significant} (p-value $< 10^{-5}$).}
\label{table:throughput_and_delay}
\end{minipage}
\end{table}

>>>>

\begin{table}
\begin{minipage}{\columnwidth}
\centering
\begin{tabular}{| r | r | r |}
\hline
& Link utilization & Queuing delay \\ \hline
Newreno & 95.6\% & 10.5 ms \\ \hline
Tonopah & 94.3\% & 33.6 ms \\ \hline
% p-value\protect\footnote{Using Welch's t-test} & 0.86 & $1.9 \times 10^{-6}$ \\ \hline
% $\frac{\text{Newreno}}{\text{Tonopah}}$ & 103\% & 321\% \\ \hline
\end{tabular}
\caption{Newreno's link utilization is 103\% Tonopah's. But the \textbf{queuing delay} of Newreno is \textbf{321\%} Tonopah's. This means that Tonopah can deliver the same throughput while cause a lot less queuing delay. The differences in \textbf{queuing delay} are \textbf{highly significant} (p-value\protect\footnote{Using Welch's t-test} $< 10^{-5}$).}
\label{table:throughput_and_delay}
\end{minipage}
\end{table}
